Everything you wanted to know about PanDA but were truly truly afraid to ask

### 2017-03-06 PandaEvolution.tex
Iteration IV

The next LHC data taking run (Run 3) will require more resources than the
Worldwide LHC Computing Grid (WLCG) can possibly provide. Currently, PanDA WMS
uses more than 100,000 cores at over 100 Grid sites, with a peak performance of
0.3 petaFLOPS. This capacity will be sufficient for the planned analysis and
data processing, but it will be insufficient for Monte Carlo (MC) production and
any extra activities. To alleviate these challenges, ATLAS is engaged in a
program to expand the current computing model to include additional resources
such as the opportunistic use of supercomputers as well as commercial and
academic clouds.

% \subsection{Use of Supercomputers with PanDA}

Modern supercomputers have been designed to mainly support parallel computation
requiring runtime communication. Job execution is parallelized across multiple
cores, each core calculating a small part of the problem and communicating with
other cores via message passing interface (MPI). Accordingly, supercomputers
have large number of worker nodes, connected through a high-speed, low-latency
network. Each worker node has multicore CPUs, usually augmented with massively
parallel Graphics Processing Units (GPUs) or other types of coprocessors.

PanDA WMS has been designed to support distributed computing. Workload or
workflow executions involves concurrent and/or sequential runs of possibly large
amount of jobs, requiring no or minimal parallelization and no communication at
runtime. Accordingly, computing infrastructure like WLCG are designed to
aggregate large amount of computing resources across sites, possibly dislocated
across multiple geographical allocation. While each site may deploy runtime
message-passing capabilities, usually these are not used to perform distributed
computations.

There are at least two approaches to enable PanDA WMS to execute ATLAS jobs on
supercomputers: using the subset of resources and capabilities shared by both
supercomputers and grid; reconciling the two paradigms of computation by means
prototype a working solution that enables computation and better understanding
of the problem space. The latter approach is principled and better suited for a
production-grade solution developed on the base of the experience accumulated
with the prototype and capable of supporting general-purpose workloads and
workflows on both supercomputers and grid infrastructures.

This section illustrates the design, architecture and execution process of the
prototype developed by the PanDA team to support execution of some of the ATLAS
workload on the Titan supercomputer. After a critical analysis of the results
obtained and the lessons learned, the following section introduces the design
and first experimental characterization of a next generation executor. This
components is designed to abstract resources and capabilities enabling the
concurrent execution of both parallel and distributed computing.

@@

The Titan supercomputer, current number two (number one from November 2012 until
June 2013) on the Top 500 list~\cite{top500} is located at the Oak Ridge
Leadership Computing Facility (OLCF) in Oak Ridge National Laboratory, US\@.
Titan is a Cray XK7 system with 18,688 compute nodes and a total of 299,008 CPU
cores. Each compute node has an AMD Opteron CPU, a Nvidia Tesla GPU, 32 GB of
RAM and no local storage, though a 16 GB RAM disk can be set up. Compute nodes
use Cray’s Gemini interconnect for inter-node MPI messaging but have no network
connection to the outside world. Titan is served by the Spider
II~\cite{spider2}, a Lustre filesystem with 32 PB of disk storage, and by a 29
PB HPSS tape storage system. Titan’s worker nodes run Compute Node Linux, a run
time environment based on SUSE Linux Enterprise Server.

@@

Titan offers to its users login nodes and data transfer nodes (DTN). Users have
to log into one of these nodes via ssh to submit jobs to Titan's PBS scheduler.
Titan's authentication and authorization model is based on two-factor
authentication with a RSA SecurID key, generated every 30 seconds. Login nodes
and DTN are the only nodes with out/inbound wide area network connectivity. Work
nodes have only local network access. Data staging is supported via the DTNs,
from the wide area network and the OLCF high performance storage system (HPSS).
DTNs are shared across all Titan's users that can schedule jobs to a dedicates
PBS batch system to automate data staging. Fair-share policies are in place both
for the batch system that for the use of DTN resources.

Titan's architecture, configuration and policies poses several challenges to the
integration with PanDA. PanDA Pilot requires to contact the Job Dispatcher
module of the PanDA Server to pull jobs to execute. Titan's work nodes do not
offer outbound network connectivity making the current deployment model of PanDA
pilots unfeasible. Titan does not support PanDA's security model based on
certificates and virtual organizations, making the PanDA's approach to identity
management also unfeasible. While DTNs offer wide area network data transfer, an
integration with ATLAS DDM is beyond the functional and administrative scope of
the current prototyping phase. Finally, the specific characteristics of the
execution environment, especially the dependences on a Lustre filesystem and on
modules tailored to Compute Node Linux, require reengineering of ATLAS
application frameworks.

Currently, no HEP application can benefit from Titan's GPUs but some
computationally-intensive, non memory-intensive tasks can be offloaded from the
grid to Titan's large amount of cores. Further, when HEP tasks can be
partitioned to independent jobs, Titan work nodes can be used to execute up to
16 concurrent jobs' payload. Given these constraints and challenges, the type of
task most suitable for execution on Titan is HEP event generation. Event
generators are mostly computational and stand-alone code, requiring less than
1GB of RAM at runtime and with small input data requirements. The event
generation in ATLAS accounts for 10--15\% of all jobs on the Grid, corresponding
to 2/3 of the current grid capacity. A more difficult workload to adapt for
Titan would be that for detector simulation. Simulation tasks tend to be tied to
the framework of a particular simulation, often requiring database access for
geometry and relevant run conditions.

\mtnote{Describe Monte Carlo workflow and Geant4 here.}

@@

The most relevant design constraint for integrating PanDA WMS and Titan is the
lack of connectivity from the work nodes. This makes impossible to port PanDA
Pilot while maintaining the defining feature of the pilot abstraction:
multi-stage scheduling to decouple resource acquisition from workload scheduling
and execution. As direct communication between PanDA Pilot and PanDA Server is
required, PanDA Pilots cannot be scheduled on Titan and jobs cannot be pulled by
a pilot from the work nodes.

Usually, this design limitation would make the integration of PanDA and Titan
unfeasible. Pilot-based executions are necessary to avoid waiting in the
supercomputer's queue to execute every single job of a distributed workload.
This is particularly true for Titan where, consistently with the intended use
case of the machine, queuing policies privilege parallel jobs on the base of the
quantities of work nodes requested. It would still be possible to execute HEP
event generation tasks but the time spent waiting in the queue would be too
large compared to the execution time.

About 10\% of Titan's capacity is unused due to mismatches between job sizes and
available resources~\cite{titan_utilization}. Worker nodes are unused because
there are not enough nodes to execute large jobs or the required amount of nodes
would not be available for a long enough time. This makes available around
30,000 cores for a total of approximately 270M core hours per
year~\cite{titan_free}, roughly 30\% of the overall capacity of WLCG. A system
that can occupy those temporarily free nodes with smaller scale tasks would be
very valuable. For this reason, Titan offers backfill functionalities: users can
interrogate Titan's Moab scheduler about how many free nodes are currently
available and for how long. If a user submit a request for that number of nodes,
queue time will be minimal.

@@

Backfill functionality offers the opportunity not to use the pilot abstraction
while still avoiding too much queue time overhead. On Titan, PanDA Pilot has
been redesigned to serve as a job broker. Architected as a stand-alone service
to be executed on a DTN, this PanDA Broker implements functionalities to: (i)
interrogate Titan about backfill availability; (ii) pull Geant4 jobs and events;
(iii) wrap Geant4 payloads into PBS MPI job; (iv) submitting PBS jobs to Titan's
batch system; and (v) staging input/output files. The new functionalities of
PanDA Broker involve backfill querying, payload wrapping, and job submission.
Functionalities for Geant4 job and events pulling, and file staging were mostly
inherited from PanDA Pilot.

@@

Backfill querying is performed via the dedicated Moab command while payload
wrapping is done via a tailored Python MPI script. This MPI wrapper serves as a
``container'' for non-MPI jobs, enabling execution of unmodified Grid-centric
jobs on Titan. Typically, a MPI wrapper is workload-specific as it sets up the
execution environment for a specific payload. This involves organization of
worker directories, data management, optional input parameters modification, and
cleanup on exit. Upon submission, a copy of the MPI wrapper runs on every
available work node. Each script knows its MPI rank (an index that runs from
zero to a maximum number of nodes or script copies) as well as the total number
of ranks in the current submission. When activated on worker nodes, each copy of
the wrapper script starts the execution of the payload in a subprocess and waits
until its completion.

MPI wrappers are submitted to Titan's PBS batch system via
RADICAL-SAGA~\cite{radical-saga}. SAGA (Simple API for Grid Applications)
provides a unified interface to diverse job schedulers and file transferring
services. SAGA provides an interoperability layer that lowers the complexity and
improves the simplicity of using distributed infrastructure. RADICAL-SAGA is a
Python module, compliant with the OGF GFD.90 SAGA
specification~\cite{saga-spec}. Behind the API façade, RADICAL-SAGA implements a
adaptor architecture: each adaptor interface the SAGA API with different
middleware systems and services, including the batch scheduler of Titan.

PanDA Broker stages capabilities are implemented via a file system shared among
DTNs and work nods. Input files that are required by the payload are downloaded
via the ATLAS DDM service and then stored in a directory on the shared
filesystem. Part of the MPI wrapper setup process is to make the location of
these files known to the payload. Payloads' output files are located on the
shared filesystem by the broker and transferred from Titan to the ATLAS Tier 1
computing center at Brookhaven National Lab (BNL). In principle any Grid site
could be used.

The execution process of Geant4 on Titan by PanDA has X steps: (i) PanDA Broker
queries Titan's Moab scheduler about currently unused nodes and checks whether
the time and size of the available backfill resources are suitable to execute
jobs of Geant4 tasks; (ii) The PanDA Broker transmits this information to the
Job Dispatcher module of the PanDA server, and in response gets a list of Geant4
jobs bound to Titan; (iii) based on the jobs attributes, the broker requests to
the Data Service module of the PanDA Server to transfer the necessary input data
via the ATLAS DDM service; (iv) once all the data is transferred, the PanDA
Broker calculates the number of cores and duration of jobs that can be submitted
to Titan on the base of the information collected about backfill resource
availability; (v) the broker creates one or more PBS MPI scripts to wrap enough
Geant4 payload to fit the calculated number and duration of cores; (vi) the
broker submits jobs to Titan's PBS batch system via RADICAL-SAGA; (vii) the PBS
jobs waits a minimal amount of time into the queue until is scheduled for
execution; (viii) upon execution on the worker nodes, the MPI script sets up the
execution environment required by the wrapped Geant4 payload, including
assembling the AthenaMP framework in ramdisk; (ix) the payload is then executed
into dedicated processes, 16 for each work node, 1 for each core; (x) the PanDA
Broker locates on the shared filesystem the output files produced by the payload
and transfer them to BNL ATLAS Tier 1 computing centre.

>>>>

The next LHC run for taking data (Run 3) will require more resources than the
Worldwide LHC Computing Grid (WLCG) can possibly provide. Currently, PanDA WMS
uses more than 100,000 cores at over 100 Grid sites, with a peak performance of
0.3 petaFLOPS. This capacity will be sufficient for the planned analysis and
data processing, but it will be insufficient for the Monte Carlo (MC) production
workflow and any extra activity. To alleviate these challenges, ATLAS is engaged
in a program to expand the current computing model to include additional
resources such as the opportunistic use of supercomputers as well as commercial
and academic clouds.

\subsection{Use of Supercomputers with PanDA}

Modern supercomputers have been designed to mainly support parallel computation
that requires runtime communication. Job execution is parallelized across
multiple cores, each core calculating a small part of the problem and
communicating with other cores via a message passing interface (MPI).
Accordingly, supercomputers have large number of worker nodes, connected through
a high-speed, low-latency dedicated network. Each worker node has multicore
CPUs, usually augmented with massively parallel Graphics Processing Units (GPUs)
or other types of specialized coprocessors.

PanDA WMS has been designed to support distributed computing. Executing
Workloads or workflows involves concurrent and/or sequential runs of possibly
large amount of jobs, each requiring no or minimal parallelization and no
communication at runtime. Accordingly, computing infrastructure like WLCG have
been designed to aggregate large amount of computing resources across sites,
often dislocated across geographical locations. While each site may deploy
runtime message-passing capabilities, usually these are not used to perform
distributed computations.

There are at least two approaches to enable PanDA WMS to execute ATLAS jobs on
supercomputers: (i) using the subset of resources and capabilities shared by
both supercomputers and Grid; (ii) reconciling the parallel and distributed
computing paradigms by means of dedicated abstractions. The former is a
pragmatic approach that enables the execution of specific workloads by
prototyping single-point solutions. The latter approach is principled and better
suited for a production-grade solution, capable of supporting general-purpose
workloads and workflows on both supercomputers and Grid infrastructures. These
two approaches are not mutually exclusive: developing a single-point solution
gives the opportunity to better understand the problem space, supporting the
creation of abstractions for the integration of computing paradigms.

This section illustrates the design, architecture and execution process of a
prototype developed by the PanDA team to support execution of the Geant4 stage
of the ATLAS production Monte Carlo workflow on the Titan supercomputer, managed
by the Oak Ridge Leadership Computing Facility (OLCF) at the Oak Ridge National
Laboratory (ORNL). After an analysis of the results obtained and the lessons
learned, the following section introduces the design and first experimental
characterization of a next generation executor (NGE). NGE is designed to
abstract resources and capabilities, enabling the concurrent execution of both
parallel and distributed computing.

@@

The Titan supercomputer, current number two
% (number one from November 2012 until June 2013)
on the Top 500 list~\cite{top500}, is a Cray XK7 system with 18,688 compute
nodes and a total of 299,008 CPU cores. Each compute node has an AMD Opteron
CPU, a Nvidia Tesla GPU, 32 GB of RAM and no local storage, though a 16 GB RAM
disk can be set up. Compute nodes use Cray’s Gemini interconnect for inter-node
MPI messaging but have no network connection to the outside world. Titan is
served by the Spider II~\cite{spider2}, a Lustre filesystem with 32 PB of disk
storage, and by a 29 PB HPSS tape storage system. Titan’s worker nodes run
Compute Node Linux, a run time environment based on SUSE Linux Enterprise
Server.

@@

Titan offers to its users login nodes and data transfer nodes (DTNs). Users have
to log into one of these nodes via ssh to submit jobs to Titan's PBS scheduler.
Titan's authentication and authorization model is based on two-factor
authentication with a RSA SecurID key, generated every 30 seconds. Login nodes
and DTNs are the only nodes with out/inbound wide area network connectivity.
Work nodes have only local network access. Data staging is supported via the
DTNs, from the wide area network and the OLCF high performance storage system
(HPSS). DTNs are shared across all Titan's users that can schedule jobs to a
dedicates PBS batch system to automate data staging. Fair-share policies are in
place both for the batch system and for the use of DTN resources.

Titan's architecture, configuration and policies poses several challenges to the
integration with PanDA. PanDA Pilot requires to contact the Job Dispatcher
module of the PanDA Server to pull jobs to execute. Titan's work nodes do not
offer outbound network connectivity, making the current deployment model of
PanDA pilots unfeasible. Titan does not support PanDA's security model based on
certificates and virtual organizations, making the PanDA's approach to identity
management also unfeasible. While DTNs offer wide area network data transfer, an
integration with ATLAS DDM is beyond the functional and administrative scope of
the current prototyping phase. Finally, the specific characteristics of the
execution environment, especially the absence of local storage on the work nodes
and modules tailored to Compute Node Linux, require reengineering of ATLAS
application frameworks.

Currently, no HEP application can benefit from Titan's GPUs but some
computationally-intensive and non memory-intensive tasks can be offloaded from
the Grid to Titan's large amount of cores. Further, when HEP tasks can be
partitioned to independent jobs, Titan work nodes can be used to execute up to
16 concurrent jobs' payload, one for each core. Given these constraints and
challenges, the type of task most suitable for execution on Titan is HEP event
generation. Event generations are mostly computational and stand-alone code,
requiring less than 1GB of RAM at runtime and with small input data
requirements. The event generation in ATLAS accounts for 10--15\% of all jobs on
the Grid, corresponding to 2/3 of the current Grid capacity. A more difficult
workload to adapt for Titan would be that for detector simulation. Simulation
tasks tend to be tied to the framework of a particular simulation, often
requiring database access for geometry and relevant run conditions.

\mtnote{Currently, is PanDA running event generation, simulation or both on Titain?}
\mtnote{Please provide a diagram illustrating event generation and simulation
stats compared to the whole ATLAS computation activity.}

Event generation and detector simulation are part of the ATLAS production Monte
Carlo (MC) workflow (also known as MC production chain)~\cite{mcworkflow}. The
MC workflow consists of four main stages: event generation, detector simulation,
digitization, and reconstruction. Even generation creates sets of particle
four-momenta via different generators, e.g., PYTHIA~\cite{herwig} and
HERWIG~\cite{herwig}. The detector simulator is called Geant4~\cite{geant4} and
simulates the interaction of these particles with the sensitive material of the
ATLAS detector. Each interaction creates a so-called hit and all hits are
collected and passed to the digitalization stage. There, hits are further
process to mimic the readout of the detector, including subtle events specific
to each detector's sub-component. Finally, the reconstruction stage operates
local pattern recognition, creating high-level objects like particles and jets.

@@

The lack of wide area network connectivity on Titan's work nodes is the most
relevant challenge for integrating PanDA WMS and Titan. Without connectivity,
Panda Pilots cannot be scheduled on work nodes because they would not be able to
communicate with PanDA Server and therefore pull and execute jobs. This makes
impossible to port PanDA Pilot to Titan while maintaining the defining feature
of the pilot abstraction: decoupling resource acquisition from workload
execution via multi-stage scheduling.

The unavailability of pilots is a potential drawback when executing distributed
workloads like MC event generation and simulation. Pilots are used to increase
the throughput of distributed workloads: while pilots have to wait in the
supercomputer's queue, once scheduled, they can pull and execute jobs avoiding
the supercomputer's queue. This is particularly relevant for machines like Titan
where queue policies privilege parallel jobs on the base of the number of work
nodes they request: the higher the number of nodes, the shorter the amount of
queue time (modulo fair share policies).

% MC event generation and simulation tasks can be executed without pilots but
% the time spent waiting in the queue would be too large compared to the
% execution time of each task.

Titan's backfill functionality offers the opportunity not to use the pilot
abstraction while still avoiding queue time overheads. At any point in time,
Titan's Moab scheduler shows how many work nodes cannot be used by the jobs
already queued: All these jobs are either too large or their walltime is too
long. By submitting a job requesting the number of free work nodes and walltime,
queue time can be avoided.

Compared to pilots, backfill has the disadvantage of limiting the amount of work
nodes that can be requested. Pilots are normal jobs: they can request as many
work nodes for as much time as a queue can offer. On the contrary, jobs sized on
the base of the backfill availability depend on the amount of work nodes that
cannot be given to any other job. Usually, this amount of work nodes is a
fraction of the total capacity of the queue but the size of Titan mitigates this
limitation. Every year, about 10\% of Titan's capacity remains
unused~\cite{titan_utilization}, for a total of 30,000 cores that correspond to
270M core hours per year, roughly 30\% of the overall capacity of WLCG.

% A system that can use those temporarily free work nodes with smaller
% scale tasks would be very valuable. For this reason, Titan offers backfill
% functionalities: users can interrogate Titan's Moab scheduler about how many
% free nodes are currently available and for how long. If a user submit a
% requestvfor that number of nodes and walltime, queue time will be minimal.

@@

Accordingly, PanDA Pilot has been redesigned to serve as a job broker On Titan.
Architected as a stand-alone service to be executed on a DTN, this PanDA Broker
implements functionalities to: (i) interrogate Titan about backfill
availability; (ii) pull MC jobs and events; (iii) wrap these jobs' payload into
PBS MPI jobs; (iv) submitting PBS jobs to Titan's batch system; and (v) staging
input/output files. Backfill querying, payload wrapping, and job submission
required a new implementation while job and events pulling, and file staging
were mostly inherited from PanDA Pilot.

@@

Backfill querying is performed via a dedicated Moab command while a tailored
Python MPI script is used to wrap job's payload. This MPI wrapper serves as a
``container'' for non-MPI jobs, enabling execution of unmodified Grid-centric
jobs on Titan. Typically, a MPI wrapper is workload-specific as it sets up the
execution environment for a specific payload. This involves organization of
worker directories, data management, optional input parameters modification, and
cleanup on exit. Upon submission, a copy of the MPI wrapper runs on every
available work node. Each script knows its MPI rank (an index that runs from
zero to a maximum number of nodes or script copies) as well as the total number
of ranks in the current submission. When activated on worker nodes, each copy of
the wrapper script starts the execution of the payload in a subprocess and waits
until its completion.

MPI wrappers are submitted to Titan's PBS batch system via
RADICAL-SAGA~\cite{radical-saga}. The Simple API for Grid Applications (SAGA)
offers a unified interface to diverse job schedulers and file transferring
services. In this way, SAGA provides an interoperability layer that lowers the
complexity of using distributed infrastructure. RADICAL-SAGA is a Python module,
compliant with the OGF GFD.90 SAGA specification~\cite{saga-spec}. Behind the
API façade, RADICAL-SAGA implements a adaptor architecture: each adaptor
interface the SAGA API with different middleware systems and services, including
the batch scheduler of Titan.

The data staging capabilities of the PanDA Broker are implemented via a file
system that is shared among DTNs and work nodes. The input files required by the
payload are downloaded via the ATLAS DDM service and then stored in a directory
on the shared filesystem. The MPI wrapper setup process includes making the
location of these files known to the payload. The PanDA Broker can locate the
Payloads' output files on the shared filesystem and transfer them from Titan to
the ATLAS Tier 1 computing center at Brookhaven National Lab (BNL) or any other
Grid site.

Once deployed, every PanDA Broker supports the execution of MC event generation
and detector simulation on Titan in 10 steps: (i) PanDA Broker queries Titan's
Moab scheduler about currently unused worker nodes;
% and checks whether the time and size of the available backfill resources are
% suitable to execute jobs;
(ii) The PanDA Broker transmits this information to the Job Dispatcher module of
the PanDA server and, in response, it gets a list of jobs that have been bound
to Titan by JEDI; (iii) based on the jobs attributes, the PanDA Broker requests
to the Data Service module of the PanDA Server to transfer the necessary input
data to the DTN via the ATLAS DDM service; (iv) once all the data are
transferred, the PanDA Broker calculates the number of cores and duration of
jobs that can be submitted to Titan on the base of the information collected
about backfill worker nodes availability; (v) the PanDA Broker creates one or
more PBS MPI scripts to wrap enough jobs' payload to fit the work nodes
available via backfill; (vi) the PanDA Broker submits these MPI jobs to the
Titan's PBS batch system via RADICAL-SAGA; (vii) the MPI jobs waits a minimal
amount of time into the queue until are scheduled for execution; (viii) upon
execution on the worker nodes, each MPI script sets up the execution environment
required by the wrapped payload, assembling a specific AthenaMP configuration in
ramdisk; (ix) the payload is executed into dedicated processes, 16 for each work
node, 1 for each core; (x) the PanDA Broker locates the output files produced by
the payload on the shared filesystem and transfer them to BNL ATLAS Tier 1
computing centre.

### 2017-03-06 paper.tex
Itartion workflow description
Inversion between WMSLiterature and Terminology
Section III
First pass IV (former IV and V) + restructuring
Iteration IV

\title{Everthing you wanted to know about PanDA but were truly truly afraid to
ask}

@@

% ----------------------------------------------------------------------------
% II - BACKGROUND AND RELATED WORK
% ----------------------------------------------------------------------------
\section{Background and Related Work}
\label{sec:bkgrd_literature}

@@

\begin{enumerate}
  \item PanDA WMS
  \begin{enumerate}
    \item State Diagrams
    \item Control Flow Diagrams
    \item Software Module and Architecture diagrams.
  \end{enumerate}
  \item PANDA Pilot
\end{enumerate}

@@

% ----------------------------------------------------------------------------
% IV - ATLAS MONTE CARLO WORKFLOW
% ----------------------------------------------------------------------------
\section{ATLAS Monte Carlo Workflow}
\label{sec:mc_workflow}

\input{workflow}

% ----------------------------------------------------------------------------
% V - DEPLOYING PANDA ON A LEADERSHIP-SCALE SYSTEM
% ----------------------------------------------------------------------------
\section{Deploying PanDA on a Leadership-scale system}
\label{sec:panda_deployment}

\begin{enumerate}
  \item Why? To support a specific stage of the ATLAS Monte Carlo Workflow.
  \item Challenges
  \item Opportunities
  \item Highlight distinction of PanDA on wide-area distributed systems vs on TITAN
  \item Take-aways, lessons learned
\end{enumerate}

\input{titan}

% ----------------------------------------------------------------------------
% VI - EVOLUTION OF PANDA WMS
% ----------------------------------------------------------------------------
% \section{Evolution of PanDA WMS}
% \label{sec:panda_evolution}

@@

% ----------------------------------------------------------------------------
% VI - PERFORMANCE CHARACTERIZATION
% ----------------------------------------------------------------------------
% \section{Performance Characterization}
% \label{sec:panda_performance}
%
% \input{perf}

% ----------------------------------------------------------------------------
% VI - PERFORMANCE CHARACTERIZATION
% ----------------------------------------------------------------------------
% \section{Putting it all together: Experience of PanDA on TITAN} % (fold)
\section{Performance Characterization}
\label{sec:panda_titan}

>>>>

\title{Everything you wanted to know about PanDA but were truly truly afraid to
ask}

@@

% ----------------------------------------------------------------------------
% II - BACKGROUND AND RELATED WORK
% ----------------------------------------------------------------------------
\section{Background and Related Work}
\label{sec:bkgrd}

@@

@@

% ----------------------------------------------------------------------------
% IV - DEPLOYING PANDA ON A LEADERSHIP-SCALE SYSTEM
% ----------------------------------------------------------------------------
\section{Deploying PanDA on a Leadership-scale system}
\label{sec:panda_deployment}

% \begin{enumerate}
%   \item Why? To support a specific stage of the ATLAS Monte Carlo Workflow.
%   \item Challenges
%   \item Opportunities
%   \item Highlight distinction of PanDA on wide-area distributed systems vs on TITAN
%   \item Take-aways, lessons learned
% \end{enumerate}

@@

% ----------------------------------------------------------------------------
% VI - PERFORMANCE CHARACTERIZATION
% ----------------------------------------------------------------------------
\section{Performance Characterization}
\label{sec:panda_titan}

### 2017-03-06 titan.tex
Iteration IV

The topology and architecture details of Spider II infrastructure are
illustrated in Figure~\ref{fig:xk7-compute-node} and
described as follows:

\begin{figure}[!htb]
    \centering
    \begin{tabular}{cc}
        {\includegraphics[width=0.48\textwidth]{figures/spider2arch.pdf}}\\
    \end{tabular}
    \caption{Infrastructure and I/O path between Titan (Cray XK7) and its backend storage}
    \label{fig:xk7-compute-node}
\end{figure}

Spider II is based on the Lustre technology~\cite{lustre}.  It is configured
and deployed as two independent, non-overlapping file systems, each with 144
Lustre Object Storage Servers (OSSs) and 1,008 Lustre Object Storage Targets
(OSTs). Spider II offers ~30 PB usable file system capacity to OLCF systems and
users and has over 1 TB/s aggregate write I/O performance.

>>>>

% The topology and architecture details of Spider II infrastructure are
% illustrated in Figure~\ref{fig:xk7-compute-node} and
% described as follows:
%
%
% \begin{figure}[!htb]
%     \centering
%     \begin{tabular}{cc}
%         {\includegraphics[width=0.48\textwidth]{figures/spider2arch.pdf}}\\
%     \end{tabular}
%     \caption{Infrastructure and I/O path between Titan (Cray XK7) and its backend storage}
%     \label{fig:xk7-compute-node}
% \end{figure}
%
%
%
% Spider II is based on the Lustre technology~\cite{lustre}.  It is configured
% and deployed as two independent, non-overlapping file systems, each with 144
% Lustre Object Storage Servers (OSSs) and 1,008 Lustre Object Storage Targets
% (OSTs). Spider II offers ~30 PB usable file system capacity to OLCF systems and
% users and has over 1 TB/s aggregate write I/O performance.
